\chapter{Future Work} \label{chap:FutureWork}

	This chapter will provide a suggestion for future work when continuing on this research next semester.

\section{Redesign of Prototype}
  
  The prototype still needs to be worked on. After conducting the usability tests, I got some new suggestion for improvements:

	{\bf Navigation}: When implementing the system, it is a need to look at the navigation in a different way. In the usability test, all the participants would like a faster way of navigation between the questions asked. One of the proposed solutions is to go automatically to the next questions with support for going back if they selected a wrong answer.

	{\bf The order of the patterns:} One of the respondents requested that it be preferable that the mobile pattern was asked for first because that was a known environment for her. In the design it is stated that is preferable to give a random order of the patterns (using a Latin Square) in order to be able to see if the ordering is impacting the way the respondents create their patterns. This needs to be looked further into when implementing the system. If would be preferable to test whether it will give a higher level of real world data when asking for the mobile patterns first.

	{\bf Icons used:} The wireframes included icons that were found on the web, and some of the icons might need to be resigned in order to illustrate its corresponding value in a better way. One example is one of the alternatives in Figure~\ref{fig:wireframe18} that is trying to illustrate the ``slide-to-unlock'' locking mechanism (the second icon on the right side).

	Besides the navigation and the order of the patterns, there was not provided any other feedback that needs to be redesigned before the implementation. The first version of the implemented system needs to go through a new usability test before starting the actual data collection.

	\section{Implementation of Prototype}

	The prototype is still not implemented, and it needs to be finished before I am able to start collecting data. I need to decide what kind of technologies that I want to use. After implementing the system, I should conduct a new usability test as described in the last chapter. One change would be to test the system on an actual smartphone, and not on paper. The results of a test would be more accurate when using the real environment of the system. The test will provide feedback on improvements before sending out the questionnaire.

	\section{Data Collection Permission}

	Before collecting data, it is required to ask for permission to do so from ``Personvernombudet for forskning''(NSD) \cite{personvernombud}. NSD is the privacy ombudsman for approximately 150 research and educational institutions in Norway, where NTNU is one of them. The data collection can start when I have granted allowance from NSD to conduct the data collection.